---
title: "KARATINA UNIVERSITY"
subtitle: "____________________"
author: ""
fontsize: 12pt
mainfont: "Times New Roman"
output: 
  pdf: 
    number-sections: false
    fig-width: 5
    fig-height: 3
format-options:
  pdf:
    documentclass: article
    include-in-header:
      text: 
        \usepackage{titling}
        \usepackage[utf8]{inputenc}
        \usepackage{amsmath}
        \pretitle{\begin{center}\includegraphics[width=2in,height=2in]{logo.png}\LARGE\\}
        \posttitle{\end{center}}
params:
  year: 2025
  date: "January 11, 2025"
  year_of_study: "THIRD YEAR"
  academic_year: "2024/2025"
  course_code: "BBM 300"
  course_title: "Government Accounting"
  exam_time: "1400 to 1600 hrs"
  degree: "BACHELOR OF BUSINESS MANAGEMENT"
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

```{r, include=FALSE}
# copy the R logo to the current directory
file.copy(file.path(R.home("doc"), "html", "logo.png"), '.')
```

\center
\textbf{UNIVERSITY REGULAR EXAMINATIONS}

\center

\center

FOR THE DEGREE OF `r params$degree`

\center


\vspace{15mm}

`r params$academic_year` ACADEMIC YEAR


`r params$year_of_study_text`

\vspace{5mm} 

\textbf{COURSE CODE}: `r toupper(params$course_code)`

\vspace{5mm} 

\textbf{COURSE TITLE}: `r toupper(params$course_title)`

\vspace{25mm}

\textbf{DATE}: `r params$month` \hfill\ **Time**: `r params$mytime`


\vspace{10mm} 

\begin{flushleft}

Instructions: 

1. Attempt \textbf{QUESTION ONE} and choose \textbf{THREE (3)} additional questions. 


\end{flushleft}

